\vspace{-15pt}
\section*{Experience}
% {\bf Tufts Idea Exchange}, {\em Co-President}, Spring 2014\\
% \vspace*{-.15in}
% \begin{itemize}[topsep=0pt, itemsep=1pt]
%   \item Read applications, interviewed, and chose seven Tufts University undergraduates to share their ideas at our April TED-style forum, together with the TEX team and my co-President.
%   \item Managed teams of speaker coaches who helped shape our speakers' ideas into a presentation.
%   \item Managed event logistics such as venue reservation and audio-visual concerns.
% \end{itemize}
% \vspace{6pt}
{\bf Tufts University Computational Biology Research Group}, {\em Researcher}, May 2013--Present\\
\vspace*{-.15in} 
\begin{itemize}[topsep=0pt,itemsep=-1pt]
    \item Worked with Professors Benjamin Hescott and Lenore Cowen on protein function prediction.
    \item Developed and implemented algorithms in Python that built upon Hescott and Cowen's Diffusion State Distance (DSD) metric to incorporat  e genetic protein-protein interaction data into function prediction.
    \item Worked with large protein interaction datasets and graph algorithms.
    \item Currently writing scientific paper describing results for submission to RECOMB 2014.
\end{itemize}
\vspace{6pt}
{\bf CollegiateText}, {\em Co-Founder and Developer}, Spring 2013--Present\\
\vspace*{-.15in}
\begin{itemize}[topsep=0pt,itemsep=-1pt]
            \item Created textbook price comparison web site for students at Tufts University (\url{http://tuftstext.com}), Brandeis University, and Bentley University.
            \item Built an efficient full stack with the help of my co-founder: custom node.js backend, textbook data API, and front-end interface. 
            \item Managed a team of student marketers at Tufts, leading to over 9,000 pageviews in the first two weeks of operation.
            \item Plans to expand include schedule planning and textbook marketplace features.
        \end{itemize}
\vspace{6pt}
{\bf Tufts University Department of Computer Science}, Fall 2012--Present\\
\vspace*{-.15in}
\begin{list1}
%\item [] Medford, Massachusetts
\item [] {\em Teaching Assistant: Data Structures, S2014}
\item [] {\em Teaching Assistant: Problem Solving by Computer, F2013}
\item [] {\em Teaching Assistant: Machine Structure and Assembly Language Programming, S2013}
\item [] {\em Teaching Assistant: Introduction to Computer Science, F2012}
\item [] {\begin{itemize}[topsep=0pt,itemsep=-1pt]
    \item Held office hours and assisted head TAs in the teaching of laboratory classes.
    \item Graded programming projects and homework.
\end{itemize}}
\vspace{6pt}

\end{list1}