\documentclass[margin,line]{res}
\usepackage{color}
\usepackage{hyperref}
\usepackage{mathcomp}
\usepackage{enumitem}

\usepackage{graphics}
\pagecolor{white}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.3in
\itemsep=0in
\parsep=0in
\headheight=-0.65in
\footskip=-1in
\textheight=10.5in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$-$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Anthony F. Cannistra \vspace*{.02in}}
\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Anthony F. Cannistra & {\it Voice:}  (401) 793-0916 \\            
10 Glen Ellen Drive & {\it E-mail:}  \href{mailto:anthony.cannistra@tufts.edu}{\nolinkurl{anthony.cannistra@tufts.edu}}\\         
Cumberland, RI 02864-5034 & {\it WWW:} \url{http://www.anthonycannistra.com}
\end{tabular}
\section{\sc Education}
{\bf Tufts University} Medford, Massachusetts USA\\
\vspace*{-.1in}
\begin{list1}
\item[] B.A. , Computer Science and Biology (expected graduation date: May 2015)
\item[] GPA: 3.53 (Dean's List all four semesters)
 %{\bf Selected Courses}
%\begin{list2}
%\item  COMP11: Introduction to Computer Science \hfill Fall 2011
%\item COMP15: Data Structures \hfill Spring 2012
%\item MATH12: Calculus II \hfill Fall 2011
%\item MATH22: Discrete Mathematics \hfill Spring 2012
%\item BIO14: Organisms and Populations with Laboratory \hfill Spring 2012
%\end{list2}
\end{list1}
{\bf Moses Brown School} Providence, Rhode Island USA \\
\vspace*{-.1in}

\begin{list1}
\item [] GPA: 3.67
\end{list1}
\section{\sc Work and Research Experience}
{\bf Tufts University Computational Biology Research Group \hfill May 2013--Present}\\
\vspace*{-.15in}
\begin{list1}
\item [] {\em Researcher}
\item [] { \begin{itemize}[topsep=0pt,itemsep=-1pt]
            \item Worked with Professors Benjamin Hescott and Lenore Cowen on protein function prediction.
            \item Developed and implemented algorithms in Python that built upon Hescott and Cowen's Diffusion State Distance (DSD) metric to incorporate genetic protein-protein interaction data into function prediction.
            \item Worked with large protein interaction datasets and graph algorithms.
            \item Wrote scientific paper describing results for submission to RECOMB 2014.
        \end{itemize}}
\end{list1}
{\bf Tufts University Department of Computer Science \hfill Fall 2012--Present}\\
\vspace*{-.15in}
\begin{list1}
%\item [] Medford, Massachusetts
\item [] {\em Teaching Assistant: Problem Solving by Computer, F2013}
\item [] {\em Teaching Assistant: Machine Structure and Assembly Language Programming, S2013}
\item [] {\em Teaching Assistant: Introduction to Computer Science, F2012}
\item [] {\begin{list2}
\item Held office hours and assisted head TAs in the teaching of laboratory classes. 
\item Graded programming projects and homework.
\end{list2}}
\end{list1}
{\bf The Laboratory of Benjamin Raphael at Brown University \hfill Summer 2012}\\
\vspace*{-.15in}
\begin{list1}
\item [] Providence, Rhode Island
\item [] {\em Computational Biology Research Assistant}
\item [] {\begin{list2}
\item Involved in algorithm design: efficient and accurate detection of genomic structural variants.
\item Tested, improved, and redesigned existing algorithms with efficiency in mind. 
\item {\em Code available at} \href{http://gasv.googlecode.com}{\nolinkurl{http://gasv.googlecode.com}}
\end{list2}}
\end{list1}


\section{\sc Leadership Positions}
\textbf{Association for Computing Machinery, Tufts Chapter \hfill Spring 2013--Present}\\
\emph{Executive Board Member}\\
\textbf{Tufts Idea Exchange \hfill Spring 2013--Present}\\
\emph{Executive Board Member}\\
{\bf Tufts University Leonard Carmichael Society} \hfill {\bf Fall 2011--Fall 2012}\\
{\em Directional Staff Member: Transportation Coordinator} 

% \begin{list2}
% \item Managed two minivans for the use of over 50 community service groups.
% \item Created and customized an online van reservation system: \url{http://lcsvan.youcanbook.me}.
% \item Facilitated the purchase of a new minivan in the Spring of 2012.
% \end{list2}
%
%{\bf Moses Brown School Debate Team} \hfill {\bf September 2010--May 2011}\\
%{\em Co-Captain}
%\begin{list2}
%\item Offered guidance to novice debaters to improve their skills.
%\item Managed teams of debaters for tournaments and ensured successful relationships between team members.
%\end{list2}

\section{\sc Computing Experience}
{\bf Software:} Adobe Photoshop, Microsoft Office Suite, Apple Software Suite, Apple XCode \\
{\bf Operating Systems:} Unix/Linux, Mac OSX, Microsoft Windows (XP, Vista, 7) \\
{\bf Programming Languages:} C, C++, Python, \verb+bash+, Scheme, JavaScript,  HTML, CSS, and \LaTeX \\
{\bf Recently Completed Projects:} { (see more here: \href{http://www.anthonycannistra.com/portfolios.html}{\nolinkurl{http://www.anthonycannistra.com}}}) 
\begin{list1}
\item []
\begin{list2}
\item \texttt{http://tuftstext.com}, a textbook price comparison tool for Tufts students

\item A Virtual Machine written in the C programming language.
\item An image compression/decompression software suite, written in the C programming language.
%\item Efficient Song Lyric Search Engine. Optimized for large databases (N $\approx$ 4,000,000). 
\item Personal website. Designed and Built using responsive CSS templates.
%\item Discrete Event Simulator: Model of Supermarket. Analyzed various checkout configurations.
%\item Modular, Object-Based Language Analyzer and Unknown Language Identifier. 
\end{list2}
\end{list1}
\section{\sc Honors and Awards}

Admission to PennApps Hackathon at the University Of Pennsylvania, 2013
\vspace*{-.15in}

Intuit Sustainability Prize -- MIT/Harvard ID Hack, 2013
\vspace*{-.15in}


College Board Advanced Placement Distinguished Scholar Award, 2011 
\vspace*{-.15in}

Admission to the National Cum Laude Society, 2011 
\vspace*{-.15in}

Rhode Island Forensic League: Best Varsity Debater, 2011





%
%{\bf  Brown University \& Memorial Hospital of Rhode Island \hfill Summer--Winter 2011}\\
%\vspace*{-.15in}
%\begin{list1}
%%\item [] Pawtucket, Rhode Island
%\item [] {\em Lung Age COPD Study Research Assistant}
%\item [] {\begin{list2}
%\item Recruited and interviewed patients over the telephone while delivering study information.
%\item Required to understand and follow United States HIPAA law.
%\end{list2}}
%\end{list1}



% \section{\sc Coursework}
% Animal Behavior, Computational Biology, Data Structures, Machine Structure/Assembly Language Programming, Discrete Mathmatics


\section{\sc Volunteer Service}
{\bf Cyclist and Fundraiser}, {\em National Multiple Sclerosis Society, Rhode Island Chapter}
\begin{list2}
\item Raised over \$8000 total in the June 2010, 2011, and 2012 150-Mile cycling tours.
\end{list2}

%\section{\sc Relevant Coursework}
%{\bf Computer Science Curriculum:}
%\begin{list2}
%\item COMP11: Introduction to Computer Science \hfill [Fall 2011]
%\item COMP15: Data Structures \hfill [Spring 2012]
%\item COMP40: Machine Structure and Assembly-Language Programming \hfill [Fall 2012]
%\item COMP105: Programming Languages \hfill [{\em In Progress}, Spring 2013]
%\item COMP167: Computational Biology \hfill [{\em In Progress}, Spring 2013]
%\end{list2}
%{\bf Biology Curriculum:}
%\begin{list2}
%\item BIO14L: Organisms and Populations with Lab \hfill [Spring 2012]
%\item BIO115: General Physiology I \hfill [Fall 2012]
%\item BIO105: Molecular Biology \hfill [{\em In Progress}, Spring 2013]
%\end{list2}

\end{resume}
\end{document}




